### 2014-10-31 fundamentals/examples.tex
helps with glossary

Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
because material is tracked as discrete objects, single-pass mixed-oxide (MOX) 
recycle is
easy to implement.  The simulation initially included one provider of fresh
uranium oxide (UOX) fuel, one recycled fuel fabrication facility, one reactor, one separations
facility, and one repository. The simulation duration was set to 1100 months.

The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
fuel materials from an arbitrary number of different sources dilineated by
commodity. Custom, non-uniform preferences can be set for each different fuel
commodity.  The dynamic resource exchange makes it easy for a reactor to
preferrentially accept recycled MOX fuel over fresh UOX fuel.  The
\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these is
as simple as editing numbers in an input file such as:

@@

\begin{figure}[H]
\label{fig:flowmodopen}
\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\end{figure}

To switch to a fully closed fuel cycle, all that needs to be done is change
the output commodity for the \Class{BatchReactor}'s spent MOX fuel.  All this
requires is a one-word change in the input file:

@@

\begin{figure}[H]
\label{fig:flowclosed}
\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-closed-1.eps}
\end{center}
\end{figure}

>>>>

Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
because material is tracked as discrete objects, single-pass \gls{MOX} 
recycle is
easy to implement.  The simulation initially included one provider of fresh
\gls{UOX} fuel, one recycled fuel fabrication facility, one reactor, one separations
facility, and one repository. The simulation duration was set to 1100 months.

The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
fuel materials from an arbitrary number of different sources dilineated by
commodity. Custom, non-uniform preferences can be set for each different fuel
commodity.  The dynamic resource exchange makes it easy for a reactor to
preferrentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  The
\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these is
as simple as editing numbers in an input file such as:

@@

\begin{figure}[H]
\label{fig:flowmodopen}
\caption{Modified open 1-pass \gls{MOX} recycle fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\end{figure}

To switch to a fully closed fuel cycle, all that needs to be done is change
the output commodity for the \Class{BatchReactor}'s spent \gls{MOX} fuel.  All this
requires is a one-word change in the input file:

@@

\begin{figure}[H]
\label{fig:flowclosed}
\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-closed-1.eps}
\end{center}
\end{figure}

### 2014-10-31 fundamentals/qa.tex
helps with glossary

Continuous integration (CI) is the idea that software should be tested and validated 
as it is being developed, rather than as a final stage in a longer development 
cycle.  Under CI every pull request is tested independently immeadiately after 
it is proposed. Such tests shoudl be run on all officially supported platforms. 
Cyclus uses a CI platform called Polyphemus \cite{scopatz_polyphemus_2014}.

@@

CI has become a neccessary but not sufficient addition to the cyclus QA
system. Its merit is that it keeps bad code out. However, cyclus will always
require human eyes and human hands to let good code in.

>>>>

\gls{CI} is the idea that software should be tested and validated 
as it is being developed, rather than as a final stage in a longer development 
cycle.  Under \gls{CI} every pull request is tested independently immeadiately after 
it is proposed. Such tests shoudl be run on all officially supported platforms. 
Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}.

@@

\gls{CI} has become a neccessary but not sufficient addition to the cyclus QA
system. Its merit is that it keeps bad code out. However, cyclus will always
require human eyes and human hands to let good code in.
